\chapter{Mid-Course Survey}\label{sec:appendix_b}
\begin{enumerate}
    \item What is your current major? \textit{(Checkboxes, select one or more)}
    \begin{enumerate}
        \item Computer Science
        \item Computer Engineering
        \item Data Science
        \item Cognitive Science
        \item Mathematics-Computer Science
        \item Bioengineering w/ Specialization in Bioinformatics
        \item Biology w/ Specialization in Bioinformatics
        \item Chemistry and Biochemistry w/ Specialization in Bioinformatics
        \item Interdisciplinary Computing and the Arts (ICAM)
        \item Other
    \end{enumerate}

    \item In which section of the course are you officially enrolled? \textit{(Multiple Choice, choose one)}
    \begin{enumerate}
        \item CSE 100 (in-person)
        \item CSE 100R (remote)
    \end{enumerate}

    \item Do you live on campus or off campus? \textit{(Multiple Choice, choose one)}
    \begin{enumerate}
        \item On campus
        \item Off campus
    \end{enumerate}

    \item Excluding Lecture 0, approximately how times did you attend a lecture, in person OR remotely, by the end of Week 5? \textit{(Multiple Choice, choose one)}
    \begin{enumerate}
        \item 0 times
        \item 1 to 5 times
        \item 6 to 10 times
        \item 11 to 15 times
    \end{enumerate}

    \item Excluding Lecture 0, approximately how many times did you attend a lecture IN PERSON by the end of Week 5? \textit{(Multiple Choice, choose one; the response to this question determined which section of the survey would come next)}
    \begin{enumerate}
        \item 0 times
        \item 1 to 5 times
        \item 6 to 10 times
        \item 11 to 15 times
    \end{enumerate}

\noindent \textbf{HYBRID, IN-PERSON ATTENDEES}

    \item Which of the following reasons have enabled you to keep attending lectures in person? \textit{(Checkboxes, select one or more)}
    \begin{enumerate}
        \item I prefer to learn in an in-person setting.
        \item It is easier for me to learn in an in-person setting.
        \item I am already near the lecture hall on those days, so it is more convenient.
        \item I enjoy the level of engagement involved in attending lectures in person.
        \item I feel more involved in the class community when I attend lectures in person.
        \item I live on/near campus.
        \item None of the above
        \item Other
    \end{enumerate}

    \item (Optional) Please elaborate on your response to the previous question. \textit{(Free Response)}

\noindent \textbf{REMOTE, ASYNCHRONOUS, NON-ATTENDEES}

    \item Which of the following reasons have prevented you from attending lectures in person? \textit{(Checkboxes, select one or more)}
    \begin{enumerate}
        \item I prefer to learn in a remote setting.
        \item It is easier for me to learn in a remote setting.
        \item I am concerned for my health during the ongoing COVID-19 pandemic.
        \item I do not have a method of transportation that allows me to get to campus.
        \item I have a scheduling conflict that prevents me from attending lectures live.
        \item The lecture hall is too far from my on-campus residence.
        \item The scheduled lecture time is too early in the day.
        \item None of the above
        \item Other
    \end{enumerate}

    \item (Optional) Please elaborate on your response to the previous question. \textit{(Free Response)}

\noindent \textbf{ALL RESPONDENTS}

    \item Approximately how many times did you attend a discussion section IN PERSON by the end of Week 5? \textit{(Short Answer, numerical from 0 to 5)}

    \item How frequently did you do the following by the end of Week 5? \textit{(Likert scale: 1–5 where 1 was labeled as ``Never'' and 5 was labeled as ``Several times a week'')}
    \begin{enumerate}
        \item watch a topic video on EdStem
        \item watch a lecture recording on EdStem
        \item watch a discussion section recording on EdStem
        \item go to tutor lab hours on Autograder
        \item go to TA office hours on Zoom
        \item submit a post to the EdStem Discussion Board
        \item read another student's post on the EdStem Discussion Board
        \item ask a question in the CSE 100/100R Discord server
    \end{enumerate}

    \item Would you be more likely to go to the tutor lab hours if they were held in person in the CSE Basement, in addition to being held over Zoom? \textit{(Multiple Choice, choose one)}
    \begin{enumerate}
        \item Yes
        \item No
        \item Not sure
    \end{enumerate}

    \item Would you be more likely to go to the TA office hours if they were held in person in the CSE Basement, in addition to being held over Zoom? \textit{(Multiple Choice, choose one)}
    \begin{enumerate}
        \item Yes
        \item No
        \item Not sure
    \end{enumerate}

    \item (Optional) What suggestions do you have for potential resources that could be made available in future offerings of CSE 100/100R? \textit{(Free Response)}

    \item Would you be willing to participate in a 30-minute-long follow-up interview over Zoom on your thoughts about CSE 100/100R? We would love to hear what you have to say! \textit{(Multiple Choice, choose one)}
    \begin{enumerate}
        \item Yes
        \item No
    \end{enumerate}
\end{enumerate}