\chapter{Pre-Course Survey}\label{sec:appendix_a}
\begin{enumerate}
    \item Which of the following CSE courses have you taken at UCSD? \textit{(Checkboxes, select one or more)}
    \begin{enumerate}
        \item CSE 8A. Introduction to Programming and Computational Problem-Solving I
        \item CSE 8B. Introduction to Programming and Computational Problem-Solving II
        \item CSE 11. Introduction to Programming and Computational Problem-Solving: Accelerated Pace
        \item CSE 12. Basic Data Structures and Object-Oriented Design
        \item CSE 15L. Software Tools and Techniques Laboratory
        \item CSE 20. Discrete Mathematics
        \item CSE 21. Mathematics for Algorithms and Systems
        \item CSE 30. Computer Organization and Systems Programming
        \item Other
    \end{enumerate}

    \item Which of the following learning tools have you used in a previous course? \textit{(Checkboxes, select one or more)}
    \begin{enumerate}
        \item Ed/EdStem (digital learning platform)
        \item Piazza (class discussion platform)
        \item Autograder (tutor queue platform)
        \item Stepik (online textbook platform)
        \item Zoom (conference call platform)
        \item None of the above
        \item Other
    \end{enumerate}

    \item In which section of the course are you officially enrolled? \textit{(Multiple Choice, choose one; the response to this question determined which section of the survey would come next)}
    \begin{enumerate}
        \item CSE 100 (in-person)
        \item CSE 100R (remote)
    \end{enumerate}

\noindent \textbf{CSE 100 (IN-PERSON)}

    \item Why did you choose to enroll in the in-person section? \textit{(Checkboxes, select one or more)}
    \begin{enumerate}
        \item I prefer to learn in an in-person setting.
        \item It is easier for me to learn in an in-person setting.
        \item I will already be on campus on those days, so it is more convenient.
        \item I am concerned that I will be unable to focus if I attend remotely.
        \item None of the above
        \item Other
    \end{enumerate}

    \item On average, how often do you plan to attend the in-person lectures? \textit{(Multiple Choice, choose one)}
    \begin{enumerate}
        \item Less than once a week
        \item Once a week
        \item Twice a week
        \item As often as possible
        \item Not sure yet
    \end{enumerate}

\noindent \textbf{CSE 100R (REMOTE)}

    \item Why did you choose to enroll in the remote section? \textit{(Checkboxes, select one or more)}
    \begin{enumerate}
        \item I prefer to learn in a remote setting.
        \item It is easier for me to learn in a remote setting.
        \item I am unable to get to campus on those days, so it is more convenient.
        \item I am concerned for my health during the ongoing COVID-19 pandemic.
        \item The in-person section was full.
        \item None of the above
        \item Other
    \end{enumerate}

    \item Do you plan to attend an in-person lecture at some point? \textit{(Multiple Choice, choose one)}
    \begin{enumerate}
        \item Yes
        \item No
        \item Not sure yet
    \end{enumerate}

\noindent \textbf{ALL RESPONDENTS}

    \item How many units are you enrolled in for this quarter? \textit{(Short Answer, numerical)}

    \item Excluding CSE 100/100R, how many of your units for this quarter are for remote courses? \textit{(Short Answer, numerical)}

    \item If CSE 100 was only offered as either an in-person or a remote course, which modality would you prefer? \textit{(Multiple Choice, choose one)}
    \begin{enumerate}
        \item Between the two, I would prefer in-person.
        \item Between the two, I would prefer remote.
        \item I have no preference.
    \end{enumerate}

    \item What is your current class standing? \textit{(Multiple Choice, choose one)}
    \begin{enumerate}
        \item 1st Year (Undergrad)
        \item 2nd Year (Undergrad)
        \item 3rd Year (Undergrad)
        \item 4th Year (Undergrad)
        \item 5th+ Year (Undergrad)
        \item Masters/PhD Student
        \item Other
    \end{enumerate}

    \item Did you enter UCSD as a transfer student from another (two-year or four-year) college or university? \textit{(Multiple Choice, choose one)}
    \begin{enumerate}
        \item Yes
        \item No
        \item N/A (I am a Masters/PhD student)
    \end{enumerate}

    \item Which gender do you most identify as? \textit{(Multiple Choice, choose one)}
    \begin{enumerate}
        \item Male
        \item Female
        \item Non-binary
        \item Prefer not to answer
        \item Other
    \end{enumerate}

    \item Do you identify as LGBTQIA+? \textit{(Multiple Choice, choose one)}
    \begin{enumerate}
        \item Yes
        \item No
        \item Prefer not to answer
        \item Other
    \end{enumerate}

    \item How would you describe yourself? \textit{(Checkboxes, select one or more)}
    \begin{enumerate}
        \item White (e.g. German, Irish, English, Italian, Polish, French)
        \item Black or African American (e.g. African American, Jamaican, Haitian, Ethiopian)
        \item Asian (e.g. Chinese, Filipino, Vietnamese, Korean, Japanese, Asian Indian)
        \item American Indian or Alaska Native (e.g. Navajo nation, Blackfeet tribe, Mayan, Aztec)
        \item Middle Eastern or North African (e.g. Lebanese, Iranian, Egyptian, Syrian, Moroccan)
        \item Native Hawaiian or Other Pacific Islander (e.g. Samoan, Chamorro, Tongan, Fijian)
        \item Prefer not to answer
        \item Other
    \end{enumerate}

    \item Are you of Hispanic, Latino, or Spanish origin? \textit{(Multiple Choice, choose one)}
    \begin{enumerate}
        \item Yes
        \item No
        \item Prefer not to answer
    \end{enumerate}
\end{enumerate}