\chapter{End-of-Course Survey}\label{sec:appendix_c}
\begin{enumerate}
    \item Approximately how times did you attend a lecture, in person OR remotely, from the start of Week 6 to the end of Week 10? (If you are taking this survey before the final lecture, you may provide an estimate.) \textit{(Multiple Choice, choose one)}
    \begin{enumerate}
        \item 0 times
        \item 1 to 5 times
        \item 6 to 10 times
        \item 11 to 15 times
    \end{enumerate}

    \item Approximately how times did you attend a lecture IN PERSON from the start of Week 6 to the end of Week 10? (If you are taking this survey before the final lecture, you may provide an estimate.) \textit{(Multiple Choice, choose one; the response to this question determined which section of the survey would come next)}
    \begin{enumerate}
        \item 0 times
        \item 1 to 5 times
        \item 6 to 10 times
        \item 11 to 15 times
    \end{enumerate}

\noindent \textbf{HYBRID, IN-PERSON ATTENDEES}

    \item Which of the following reasons have enabled you to keep attending lectures in person? \textit{(Checkboxes, select one or more)}
    \begin{enumerate}
        \item I prefer to learn in an in-person setting.
        \item It is easier for me to learn in an in-person setting.
        \item I am already near the lecture hall on those days, so it is more convenient.
        \item I enjoy the level of engagement involved in attending lectures in person.
        \item I feel more involved in the class community when I attend lectures in person.
        \item I live on/near campus.
        \item None of the above
        \item Other
    \end{enumerate}

    \item (Optional) Please elaborate on your response to the previous question. \textit{(Free Response)}

\noindent \textbf{REMOTE, ASYNCHRONOUS, NON-ATTENDEES}

    \item Which of the following reasons have prevented you from attending lectures in person? \textit{(Checkboxes, select one or more)}
    \begin{enumerate}
        \item I prefer to learn in a remote setting.
        \item It is easier for me to learn in a remote setting.
        \item I am concerned for my health during the ongoing COVID-19 pandemic.
        \item I do not have a method of transportation that allows me to get to campus.
        \item I have a scheduling conflict that prevents me from attending lectures live.
        \item The lecture hall is too far from my on-campus residence.
        \item The scheduled lecture time is too early in the day.
        \item The ongoing TA strike has made it harder to come to campus.
        \item None of the above
        \item Other
    \end{enumerate}

    \item (Optional) Please elaborate on your response to the previous question. \textit{(Free Response)}

\noindent \textbf{ALL RESPONDENTS}

    \item How frequently did you do the following by the end of Week 5? \textit{(Likert scale: 1–5 where 1 was labeled as ``Never'' and 5 was labeled as ``Several times a week'')}
    \begin{enumerate}
        \item watch a topic video on EdStem
        \item watch a lecture recording on EdStem
        \item watch a discussion section recording on EdStem
        \item go to tutor lab hours on Autograder
        \item go to TA office hours on Zoom
        \item submit a post to the EdStem Discussion Board
        \item read another student's post on the EdStem Discussion Board
        \item ask a question in the CSE 100/100R Discord server
    \end{enumerate}

    \item How frequently did you do the following by the end of Week 5? \textit{(Likert scale: 1–5 where 1 was labeled as ``Very unhelpful'' and 5 was labeled as ``Very helpful''; another option was ``I never used this resource.'')}
    \begin{enumerate}
        \item topic videos on EdStem
        \item lecture recordings on EdStem
        \item discussion recordings on EdStem
        \item tutor lab hours on Autograder
        \item TA office hours on Zoom
        \item posts on the EdStem Discussion Board
        \item questions in the Discord server
    \end{enumerate}

    \item After learning about each of the following topics in CSE 100/100R, how much did you understand them? \textit{(Likert scale: 1–5 where 1 was labeled as ``What is this?'' and 5 was labeled as ``I fully understood this topic.'')}
    \begin{enumerate}
        \item C++ Syntax \& Iterators
        \item Time \& Space Complexity
        \item Binary Search Trees (BSTs)
        \item Treaps \& Randomized Search Trees (RSTs)
        \item AVL Trees \& Red-Black Trees
        \item Multiway Tries (MWTs)
        \item Ternary Search Trees (TSTs)
        \item Hash Tables \& Hash Maps
        \item Collision Resolution Strategies
        \item Bloom Filters \& Count-Min Sketches
        \item Aho-Corasick Automatons
        \item Suffix Arrays
        \item Burrows-Wheeler Transforms (BWTs)
        \item Huffman Coding
        \item Bitwise Input/Output
        \item Graphs \& Dijkstra's Algorithm
        \item Minimum Spanning Trees
        \item Disjoint Sets
    \end{enumerate}

    \item If you were able to go back in time, would you choose to enroll in this offering of CSE 100/100R again? \textit{(Multiple Choice, choose one)}
    \begin{enumerate}
        \item Yes, I would enroll in CSE 100.
        \item Yes, I would enroll in CSE 100R.
        \item No, I would not enroll in CSE 100/100R.
        \item I am unsure.
    \end{enumerate}

    \item (Optional) In what ways did CSE 100/100R differ from your expectations for the course? \textit{(Free Response)}

    \item (Optional) What suggestions do you have for changes to CSE 100/100R that would make the course more accessible for different groups of students? \textit{(Free Response)}
\end{enumerate}